---
title: "Untitled"
author: "Simon Joyce"
date: "August 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Load libraries
```{r, include=FALSE}
library(tidyverse)
#library(car)
library(caret)
```
### Load Data
```{r, include=FALSE}
train = read_csv("train.csv")
test = read_csv("test.csv")
```
## format data for gbm
```{r}
names(train) = gsub("1st", "First", names(train))
names(train) = gsub("2nd", "Second", names(train))
names(train) = gsub("3Ssn", "ThreeSsn", names(train))
train$MSSubClass = as.factor(train$MSSubClass)
train$MSZoning = as.factor(train$MSZoning)
train$Street = factor(train$Street, levels = c("Grvl", "Pave"), ordered = TRUE)
train$Alley = ifelse(is.na(train$Alley), "None", train$Alley)
train$Alley = factor(train$Alley, levels = c("None","Grvl","Pave"), ordered = TRUE)
train$LotShape = as.factor(train$LotShape) #order was not important based on discussion?
train$LandContour = as.factor(train$LandContour)
train$Utilities = factor(train$Utilities, levels = c("NoSeWa", "AllPub"), ordered = TRUE)
train$LotConfig = as.factor(train$LotConfig)
train$LandSlope = factor(train$LandSlope, levels = c("Gtl", "Mod", "Sev"), ordered = TRUE)
train$Neighborhood = as.factor(train$Neighborhood)
train$Condition1 = as.factor(train$Condition1)
train$Condition2 = as.factor(train$Condition2)
train$BldgType = as.factor(train$BldgType)
train$HouseStyle = as.factor(train$HouseStyle)
train$RoofStyle = as.factor(train$RoofStyle)
train$RoofMatl = as.factor(train$RoofMatl)
train$ExteriorFirst = as.factor(train$ExteriorFirst)
train$ExteriorSecond = as.factor(train$ExteriorSecond)
train$MasVnrType = as.factor(train$MasVnrType)
train$ExterQual = factor(train$ExterQual , levels = c("Po", "Fa", "TA", "Gd", "Ex"), ordered = TRUE)
train$ExterCond = factor(train$ExterCond , levels = c("Po", "Fa", "TA", "Gd", "Ex"), ordered = TRUE)
train$Foundation = as.factor(train$Foundation)
train$BsmtQual = ifelse(is.na(train$BsmtQual), "None", train$BsmtQual)
train$BsmtQual = factor(train$BsmtQual , levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"), ordered = TRUE)
train$BsmtCond = ifelse(is.na(train$BsmtCond), "None", train$BsmtCond)
train$BsmtCond = factor(train$BsmtCond , levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"), ordered = TRUE)
train$BsmtExposure= ifelse(is.na(train$BsmtExposure), "None", train$BsmtExposure)
train$BsmtExposure = factor(train$BsmtExposure , levels = c("None", "No", "Mn",   "Av", "Gd"), ordered = TRUE)
train$BsmtFinType1 = ifelse(is.na(train$BsmtFinType1), "None", train$BsmtFinType1)
train$BsmtFinType1 = factor(train$BsmtFinType1 , levels = c("None", "Unf", "LwQ", "Rec", "BLQ", "ALQ", "GLQ"), ordered = TRUE)
train$BsmtFinType2 = ifelse(is.na(train$BsmtFinType2), "None", train$BsmtFinType2)
train$BsmtFinType2 = factor(train$BsmtFinType2 , levels = c("None", "Unf", "LwQ", "Rec", "BLQ", "ALQ", "GLQ"), ordered = TRUE)
train$Heating = as.factor(train$Heating)
train$HeatingQC = factor(train$HeatingQC , levels = c("Po", "Fa", "TA", "Gd", "Ex"), ordered = TRUE)
train$CentralAir = as.factor(train$CentralAir)
train$Electrical = as.factor(train$Electrical)
train$KitchenQual = factor(train$KitchenQual , levels = c("Po", "Fa", "TA", "Gd", "Ex"), ordered = TRUE)
train$Functional = factor(train$Functional , levels = c("Sev", "Maj2", "Maj1", "Mod", "Min2", "Min1", "Typ"), ordered = TRUE)
train$FireplaceQu = ifelse(is.na(train$FireplaceQu), "None", train$FireplaceQu)
train$FireplaceQu = factor(train$FireplaceQu , levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"), ordered = TRUE)
train$GarageType = ifelse(is.na(train$GarageType), "None", train$GarageType)
train$GarageType = as.factor(train$GarageType)
train$GarageYrBlt = ifelse(is.na(train$GarageYrBlt), 0, train$GarageYrBlt)
train$GarageFinish = ifelse(is.na(train$GarageFinish), "None", train$GarageFinish)
train$GarageFinish = factor(train$GarageFinish , levels = c("None", "Unf", "RFn", "Fin"), ordered = TRUE)
train$GarageQual = ifelse(is.na(train$GarageQual), "None", train$GarageQual)
train$GarageQual = factor(train$GarageQual , levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"), ordered = TRUE)
train$GarageCond = ifelse(is.na(train$GarageCond), "None", train$GarageCond)
train$GarageCond = factor(train$GarageCond , levels = c("None", "Po", "Fa", "TA", "Gd", "Ex"), ordered = TRUE)
train$PavedDrive = factor(train$PavedDrive , levels = c("N", "P", "Y"), ordered = TRUE)
train$PoolQC = ifelse(is.na(train$PoolQC), "None", train$PoolQC)
train$PoolQC = factor(train$PoolQC , levels = c("None", "Fa", "TA", "Gd", "Ex"), ordered = TRUE)
train$Fence = ifelse(is.na(train$Fence), "None", train$Fence)
train$Fence = factor(train$Fence , levels = c("None", "MnWw", "GdWo", "MnPrv", "GdPrv"), ordered = TRUE)
train$MiscFeature = as.factor(train$MiscFeature)
train$MoSold = as.factor(train$MoSold)
train$SaleType = as.factor(train$SaleType)
train$SaleCondition = as.factor(train$SaleCondition)
train$SalePrice = log(train$SalePrice)
```

### GBM
```{r}
library(gbm)
set.seed(0)
boostTrain = gbm(SalePrice ~ . -Id,
                 data = train,
                 n.trees = 10000,
                 shrinkage = 0.001)
relative.influence(boostTrain, sort. = T)
```
### Random Forest
```{r}
library(randomForest)

set.seed(0)
forestTrain = randomForest(data = train,
                           SalePrice ~ . - Id - MiscFeature - LotFrontage ,
                           importance = T,
                           na.action=na.omit)
varImpPlot(forestTrain)
imp = importance(forestTrain, type = 1) %>%  
  abs() 
cbind(rownames(imp)[order(imp, decreasing = T)], sort(imp, decreasing = T))
```
### EDA for spreadsheet
GarageCars
```{r}
train %>% 
  select(GarageCars, SalePrice) %>% 
  ggplot(aes(x = as.factor(GarageCars), y = SalePrice)) +
  geom_boxplot()
sum(train$GarageCars == 4)
sum(train$GarageCars == 0)
```
GarageArea
```{r}
train %>% 
  select(GarageArea, SalePrice) %>% 
  filter(GarageArea > 0) %>% 
  ggplot(aes(x = GarageArea, y = SalePrice)) +
  geom_point() +
  geom_smooth()
```
GarageQual
```{r}
train %>% 
  select(GarageQual, SalePrice) %>% 
  ggplot(aes(x = GarageQual, y = SalePrice)) +
  geom_boxplot()
```
GarageCond
```{r}
train %>% 
  select(GarageCond, SalePrice) %>% 
  ggplot(aes(x = GarageCond, y = SalePrice)) +
  geom_boxplot()
```
PavedDrive
```{r}
train %>% 
  select(PavedDrive, SalePrice) %>% 
  ggplot(aes(x = PavedDrive, y = SalePrice)) +
  geom_boxplot()
```
WoodDeckSf
```{r}
hist(train$WoodDeckSF[train$WoodDeckSF > 0])
train %>% 
  select(WoodDeckSF, SalePrice) %>%
  filter(WoodDeckSF > 0) %>% 
  ggplot(aes(x = WoodDeckSF, y = SalePrice)) +
  geom_point() +
  geom_smooth()
t.test(train$SalePrice[train$WoodDeckSF > 0], train$SalePrice[train$WoodDeckSF == 0])
```
OpenPorchSF
```{r}
hist(train$OpenPorchSF)
sum(train$OpenPorchSF == 0)
train %>% 
  transmute(OpenPorchSF = (OpenPorchSF) ** (1/2), SalePrice = SalePrice) %>%
  #filter(between(OpenPorchSF, 1, 400)) %>% 
  ggplot(aes(x = OpenPorchSF, y = SalePrice)) +
  geom_point() +
  geom_smooth()
```
EnclosedPorch
```{r}
hist(train$EnclosedPorch)
summary(as.factor(ifelse(train$EnclosedPorch > 0, "Yes", "No")))
train %>% 
  transmute(EnclosedPorch = ifelse(EnclosedPorch > 0, "Yes", "No"),
            SalePrice = SalePrice) %>% 
  ggplot(aes(x = EnclosedPorch, y = SalePrice)) +
  geom_boxplot()
train %>% 
  select(EnclosedPorch, SalePrice) %>% 
  ggplot(aes(x = EnclosedPorch, y = SalePrice)) +
  geom_point() +
  geom_smooth()
train %>% 
  select(EnclosedPorch, SalePrice) %>% 
  filter(EnclosedPorch > 0) %>% 
  ggplot(aes(x = EnclosedPorch, y = SalePrice)) +
  geom_point() +
  geom_smooth()
t.test(train$SalePrice[train$EnclosedPorch > 0], train$SalePrice[train$EnclosedPorch == 0])
```
ThreeSsnPorch
```{r}
hist(train$ThreeSsnPorch)
sum(train$ThreeSsnPorch == 0)
```
ScreenPorch
```{r}
hist(train$ScreenPorch)
sum(train$ScreenPorch == 0)
t.test(train$SalePrice[train$ScreenPorch > 0], train$SalePrice[train$ScreenPorch == 0])
train %>% 
  transmute(ScreenPorch = ifelse(ScreenPorch > 0, "Yes", "No"),
            SalePrice = SalePrice) %>% 
  ggplot(aes(x = ScreenPorch, y = SalePrice)) +
  geom_boxplot()
train %>% 
  select(ScreenPorch, SalePrice) %>% 
#  filter(ScreenPorch > 0) %>% 
  ggplot(aes(x = ScreenPorch, y = SalePrice)) +
  geom_point() +
  geom_smooth()
```
PoolArea
```{r}
hist(train$PoolArea)
sum(train$PoolArea == 0)
```
Fence
```{r}
train %>% 
  select(Fence, SalePrice) %>% 
  ggplot(aes(x = Fence, y = SalePrice)) +
  geom_boxplot()
summary(train$Fence)
aov(SalePrice ~ Fence, train) %>% 
  summary()
```
MiscFeature
```{r}
summary(train$MiscFeature)
```
MoSold
```{r}
train %>% 
  select(MoSold, SalePrice) %>% 
  ggplot(aes(x = MoSold, y = SalePrice)) +
  geom_boxplot()
summary(train$MoSold)
summary(aov(SalePrice ~ MoSold, train))
oneway.test(SalePrice ~ MoSold, train, var.equal = FALSE)
```
YrSold
```{r}
train %>% 
  select(YrSold, SalePrice) %>% 
  ggplot(aes(x = as.factor(YrSold), y = SalePrice)) +
  geom_boxplot()
summary(as.factor(train$YrSold))
```
SaleType
```{r}
train %>% 
  select(SaleType, SalePrice) %>% 
  ggplot(aes(x = SaleType, y = SalePrice)) +
  geom_boxplot()
summary(train$SaleType)
```
SaleCondition
```{r}
train %>% 
  select(SaleCondition, SalePrice) %>% 
  ggplot(aes(x = SaleCondition, y = SalePrice)) +
  geom_boxplot()
summary(train$SaleCondition)
summary(aov(SalePrice ~ SaleCondition, train))
```
### Porch Feature
```{r}
trainClean %>% 
  transmute(OpenPorchSF = ifelse(OpenPorchSF == 0,
                                 NA,
                                 OpenPorchSF),
            EnclosedPorch = ifelse(EnclosedPorch == 0,
                                 NA,
                                 EnclosedPorch),
            ThreeSsnPorch= ifelse(ThreeSsnPorch == 0,
                                 NA,
                                 ThreeSsnPorch),
            ScreenPorch = ifelse(ScreenPorch == 0,
                                 NA,
                                 ScreenPorch),
            SalePrice = SalePrice) %>% 
    ggplot(aes(y = SalePrice)) +
  geom_point(aes(x = OpenPorchSF), col = "red") +
  geom_point(aes(x = EnclosedPorch), col = "green") +
  geom_point(aes(x = ScreenPorch), col = "blue") +
  geom_point(aes(x = ThreeSsnPorch))
totalPorches = trainClean %>% 
  transmute(porches = ifelse(OpenPorchSF > 0, 1, 0) +
              ifelse(EnclosedPorch > 0, 1, 0) +
              ifelse(ThreeSsnPorch > 0, 1, 0) +
              ifelse(ScreenPorch > 0, 1, 0))
(totalPorches$porches > 1) %>% sum()
(totalPorches$porches == 0) %>% sum()
(totalPorches$porches > 2) %>% sum()
trainClean %>% transmute(
  porchSF = OpenPorchSF + EnclosedPorch + ThreeSsnPorch + ScreenPorch,
  SalePrice = SalePrice
) %>% 
  ggplot(aes(x = porchSF, y = SalePrice)) + 
  geom_point() +
  geom_smooth()
trainClean[totalPorches$porches > 1, ] %>%
  select(OpenPorchSF, EnclosedPorch, ThreeSsnPorch, ScreenPorch) %>% 
  View()
trainPorch = trainClean %>%
  mutate(porch =
           if_else(totalPorches > 1, "Multi",
                   if_else(OpenPorchSF > 0, "Open",
                           if_else(EnclosedPorch > 0, "Enclosed",
                                   if_else(ThreeSsnPorch > 0, "ThreeSsn",
                                           if_else(ScreenPorch > 0, "Screen",
                                                   "None"))))) %>% 
  factor(levels = c("None", "Enclosed", "ThreeSsn", "Screen", "Open", "Multi"),
         ordered = TRUE))
 
ggplot(trainPorch, aes(x = porch, y = SalePrice)) +
  geom_boxplot()

oneway.test(data = trainPorch, SalePrice ~ porch)

trainClean %>% 
  mutate(
    porch = ifelse(OpenPorchSF + EnclosedPorch + ThreeSsnPorch + ScreenPorch > 0, "Yes", "No") %>% as.factor()
  ) %>% 
  ggplot(aes(x = porch, y = SalePrice)) +
  geom_boxplot()
```

LotAreaOutliers = c(250, 314, 336)
outliers0 = c(524, 1062, 1299)

```{r}
trainClean = train %>%
  transmute(
    MSSubClass = as.factor(MSSubClass),
    MSZoning = as.factor(MSZoning),
    LotFrontage = LotFrontage,
    LotArea = LotArea,
    LotShape = if_else(LotShape == "Reg", "Reg", "IR") %>%
      as.factor(),
    LandContour = as.factor(LandContour),
    LotConfig = if_else(LotConfig == "FR3", "FR2", LotConfig) %>%
      as.factor(),
    Neighborhood = as.factor(Neighborhood),
    Condition1 = as.factor(Condition1),
    BldgType = as.factor(BldgType),
    HouseStyle = as.factor(HouseStyle),
    OverallQual = OverallQual,
    OverallCond = ifelse(OverallCond > 5, 5, OverallCond),
    YearBuilt = YearBuilt,
    YearBuilt2 = YearBuilt ** 2,
    RoofStyle = as.factor(RoofStyle),
    Exterior_1st = if_else(Exterior1st < 20, "other", Exterior1st) %>%
      as.factor(),
    Exterior_2nd = if_else(Exterior1st != Exterior2nd, "Y", "N") %>%
      as.factor(),
    MasVnrType = if_else(is.na(MasVnrType), "None", MasVnrType) %>%
      as.factor(),
    MasVnrArea = ifelse(is.na(MasVnrArea), 0, MasVnrArea),
    ExterQual = factor(ExterQual,
                       levels = c("Po", "Fa", "TA", "Gd", "Ex"),
                       ordered = TRUE),
    ExterCond = factor(ExterCond,
                       levels = c("Po", "Fa", "TA", "Gd", "Ex"),
                       ordered = TRUE),
    Foundation = as.factor(Foundation),
    BsmtQual = if_else(is.na(BsmtQual), "nan", BsmtQual) %>%
      factor(levels = c("nan", "Po", "Fa", "TA", "Gd", "Ex"),
             ordered = TRUE),
    BsmtCond = if_else(is.na(BsmtCond), "nan", BsmtCond) %>%
      factor(levels = c("nan", "Po", "Fa", "TA", "Gd", "Ex"),
             ordered = TRUE),
    BsmtExposure= if_else(is.na(BsmtExposure), "nan", BsmtExposure) %>%
      factor(levels = c("nan", "No", "Mn", "Av", "Gd"), ordered = TRUE),
    BsmtFinType1 = if_else(is.na(BsmtFinType1), "nan", BsmtFinType1) %>%
      factor(levels = c("nan", "Unf", "LwQ", "Rec", "BLQ", "ALQ", "GLQ"),
             ordered = TRUE),
   BsmtFinSF_1 = BsmtFinSF1,
   BsmtUnfSF = BsmtUnfSF,
   TotalBsmtSF = TotalBsmtSF,
   HeatingQC = factor(HeatingQC, levels = c("Po", "Fa", "TA", "Gd", "Ex"),
                      ordered = TRUE),
   CentralAir = as.factor(CentralAir),
   Electrical = if_else(Electrical == "SBrkr", "SBrkr",
                        "other",
                        missing = "other") %>%
     as.factor(),
   FlrSF = `1stFlrSF` + `2ndFlrSF`,
   Floors = if_else(`2ndFlrSF` > 0, 2, 1),
   GrLivArea = GrLivArea,
   BsmtFullBath = if_else(BsmtFullBath > 0, "Y", "N") %>%
     as.factor(),
   FullBath = ifelse(FullBath < 2, 1, FullBath),
   HalfBath = if_else(HalfBath == 0, "N", "Y") %>%
     as.factor(),
   BedroomAbvGr = if_else(
     BedroomAbvGr < 2, 1,
     ifelse(BedroomAbvGr > 4, 5,
             BedroomAbvGr)) %>%
     as.factor(),
   KitchenAbvGr = ifelse(KitchenAbvGr < 2, 1, 2),
   KitchenQual = factor(KitchenQual,
                        levels = c("Po", "Fa", "TA", "Gd", "Ex"),
                        ordered = TRUE),
   TotRmsAbvGrd = TotRmsAbvGrd,
   Functional = if_else(Functional == "Typ", "Y", "N") %>% 
     as.factor(),
   Fireplaces = ifelse(Fireplaces > 1, 2, Fireplaces),
   FireplaceQu = if_else(is.na(FireplaceQu), "nan", FireplaceQu) %>%
     factor(levels = c("nan", "Po", "Fa", "TA", "Gd", "Ex"),
            ordered = TRUE),
   GarageType = if_else(is.na(GarageType), "None", GarageType) %>%
     as.factor(),
   GarageYrBlt = if_else(is.na(GarageYrBlt), YearBuilt, GarageYrBlt),
   GarageFinish = if_else(is.na(GarageFinish), "None", GarageFinish) %>%
     factor(levels = c("None", "Unf", "RFn", "Fin"), ordered = TRUE),
   GarageCars = ifelse(GarageCars > 2, 3, GarageCars),
   GarageArea = GarageArea,
   PavedDrive = factor(PavedDrive,
                       levels = c("N", "P", "Y"),
                       ordered = TRUE),
   WoodDeckSF = WoodDeckSF,
   OpenPorchSF = OpenPorchSF,
   EnclosedPorch = EnclosedPorch,
   ThreeSsnPorch = `3SsnPorch`,
   ScreenPorch = ScreenPorch,
   Pool = if_else(PoolArea > 0, "Y", "N") %>%
     as.factor(),
   Fence = if_else(is.na(Fence), "None", Fence) %>%
     factor(levels = c("MnWw", "GdWo", "MnPrv", "GdPrv", "None"),
            ordered = TRUE),
   MoSold = as.factor(MoSold),
   SaleType = if_else(SaleType == "New", "New", "other") %>%
     as.factor(),
   SaleCondition = if_else(
     SaleCondition == "Abnorml", "Abnorml",
     if_else(SaleCondition == "Partial", "Partial",
             "Normal")) %>% 
     as.factor(),
   SalePrice = log(SalePrice)
  )

testClean = test %>%
  transmute(
    MSSubClass =ifelse(MSSubClass == 150, 20, MSSubClass) %>% 
      as.factor(),
    MSZoning = ifelse(is.na(MSZoning), "RL", MSZoning) %>% 
      as.factor(),
    LotFrontage = LotFrontage,
    LotArea = LotArea,
    LotShape = if_else(LotShape == "Reg", "Reg", "IR") %>%
      as.factor(),
    LandContour = as.factor(LandContour),
    LotConfig = if_else(LotConfig == "FR3", "FR2", LotConfig) %>%
      as.factor(),
    Neighborhood = as.factor(Neighborhood),
    Condition1 = as.factor(Condition1),
    BldgType = as.factor(BldgType),
    HouseStyle = as.factor(HouseStyle),
    OverallQual = OverallQual,
    OverallCond = ifelse(OverallCond > 5, 5, OverallCond),
    YearBuilt = YearBuilt,
    YearBuilt2 = YearBuilt ** 2,
    RoofStyle = as.factor(RoofStyle),
    Exterior_1st = ifelse(is.na(Exterior1st), "VinylSd", Exterior1st),
    Exterior_2nd = ifelse(Exterior1st != Exterior2nd & !is.na(Exterior2nd), "Y", "N") %>%
      as.factor(),
    MasVnrType = if_else(is.na(MasVnrType), "None", MasVnrType) %>%
      as.factor(),
    MasVnrArea = ifelse(is.na(MasVnrArea), 0, MasVnrArea),
    ExterQual = factor(ExterQual,
                       levels = c("Po", "Fa", "TA", "Gd", "Ex"),
                       ordered = TRUE),
    ExterCond = factor(ExterCond,
                       levels = c("Po", "Fa", "TA", "Gd", "Ex"),
                       ordered = TRUE),
    Foundation = as.factor(Foundation),
    BsmtQual = if_else(is.na(BsmtQual), "nan", BsmtQual) %>%
      factor(levels = c("nan", "Po", "Fa", "TA", "Gd", "Ex"),
             ordered = TRUE),
    BsmtCond = if_else(is.na(BsmtCond), "nan", BsmtCond) %>%
      factor(levels = c("nan", "Po", "Fa", "TA", "Gd", "Ex"),
             ordered = TRUE),
    BsmtExposure= if_else(is.na(BsmtExposure), "nan", BsmtExposure) %>%
      factor(levels = c("nan", "No", "Mn", "Av", "Gd"), ordered = TRUE),
    BsmtFinType1 = if_else(is.na(BsmtFinType1), "nan", BsmtFinType1) %>%
      factor(levels = c("nan", "Unf", "LwQ", "Rec", "BLQ", "ALQ", "GLQ"),
             ordered = TRUE),
   BsmtFinSF_1 = BsmtFinSF1,
   BsmtUnfSF = BsmtUnfSF,
   TotalBsmtSF = TotalBsmtSF,
   HeatingQC = factor(HeatingQC, levels = c("Po", "Fa", "TA", "Gd", "Ex"),
                      ordered = TRUE),
   CentralAir = as.factor(CentralAir),
   Electrical = if_else(Electrical == "SBrkr", "SBrkr",
                        "other",
                        missing = "other") %>%
     as.factor(),
   FlrSF = `1stFlrSF` + `2ndFlrSF`,
   Floors = if_else(`2ndFlrSF` > 0, 2, 1),
   GrLivArea = GrLivArea,
   BsmtFullBath = if_else(BsmtFullBath > 0 & !is.na(BsmtFullBath), "Y", "N") %>%
     as.factor(),
   FullBath = ifelse(FullBath < 2, 1, FullBath),
   HalfBath = if_else(HalfBath == 0, "N", "Y") %>%
     as.factor(),
   BedroomAbvGr = if_else(
     BedroomAbvGr < 2, 1,
     ifelse(BedroomAbvGr > 4, 5,
             BedroomAbvGr)) %>%
     as.factor(),
   KitchenAbvGr = ifelse(KitchenAbvGr < 2, 1, 2),
   KitchenQual = ifelse(is.na(KitchenQual), "TA", KitchenQual) %>% 
     factor(levels = c("Po", "Fa", "TA", "Gd", "Ex"), ordered = TRUE),
   TotRmsAbvGrd = TotRmsAbvGrd,
   Functional = if_else(Functional == "Typ" & !is.na(Functional), "Y", "N") %>% 
     as.factor(),
   Fireplaces = ifelse(Fireplaces > 1, 2, Fireplaces),
   FireplaceQu = if_else(is.na(FireplaceQu), "nan", FireplaceQu) %>%
     factor(levels = c("nan", "Po", "Fa", "TA", "Gd", "Ex"),
            ordered = TRUE),
   GarageType = if_else(is.na(GarageType), "None", GarageType) %>%
     as.factor(),
   GarageYrBlt = if_else(is.na(GarageYrBlt), YearBuilt, GarageYrBlt),
   GarageFinish = if_else(is.na(GarageFinish), "None", GarageFinish) %>%
     factor(levels = c("None", "Unf", "RFn", "Fin"), ordered = TRUE),
   GarageCars = ifelse(GarageCars > 2, 3, GarageCars),
   GarageArea = GarageArea,
   PavedDrive = factor(PavedDrive,
                       levels = c("N", "P", "Y"),
                       ordered = TRUE),
   WoodDeckSF = WoodDeckSF,
   OpenPorchSF = OpenPorchSF,
   EnclosedPorch = EnclosedPorch,
   ThreeSsnPorch = `3SsnPorch`,
   ScreenPorch = ScreenPorch,
   Pool = if_else(PoolArea > 0, "Y", "N") %>%
     as.factor(),
   Fence = if_else(is.na(Fence), "None", Fence) %>%
     factor(levels = c("MnWw", "GdWo", "MnPrv", "GdPrv", "None"),
            ordered = TRUE),
   MoSold = as.factor(MoSold),
   SaleType = if_else(SaleType == "New" & !is.na(SaleType), "New", "other") %>%
     as.factor(),
   SaleCondition = if_else(
     SaleCondition == "Abnorml", "Abnorml",
     if_else(SaleCondition == "Partial", "Partial",
             "Normal")) %>% 
     as.factor()
  )
```
### GBM
```{r}
set.seed(0)
boostTrain = gbm(SalePrice ~ .,
                 data = trainClean,
                 n.trees = 10000,
                 shrinkage = 0.001)
relative.influence(boostTrain, sort. = T)
```
### Random Forest
```{r}
library(randomForest)

set.seed(0)
forestTrain = randomForest(data = trainClean,
                           SalePrice ~ . - LotFrontage ,
                           importance = T,
                           na.action=na.omit)
varImpPlot(forestTrain)
imp = importance(forestTrain, type = 1) %>%  
  abs() 
cbind(rownames(imp)[order(imp, decreasing = T)], sort(imp, decreasing = T))
```
### Lasso
```{r}
lambdaGrid = 10^seq(0, -4, length = 100)
alphaGrid = seq(0, 1, 100)
set.seed(0)
trainControl = trainControl(method = 'cv', number=10)
tuneGrid = expand.grid(lambda = grid, alpha=alphaGrid)
ridgeTrain = train(data = trainClean[, -3],
                    SalePrice ~ .,
                    method = 'glmnet',
                    trControl = trainControl,
                    tuneGrid = tuneGrid)
plot(ridgeTrain, xTrans=log)
varImp(ridgeTrain)
ridgeTrain$bestTune
coef(ridgeTrain$finalModel)
```

```{r}
library(glmnet)
grid = 10^seq(0, -3, length = 100)
x = model.matrix(SalePrice ~ ., trainClean[, -3])[, -1]
lassoTrain = glmnet(x,
                      trainClean$SalePrice,
                      alpha = 1, lambda = grid)

#Visualizing the ridge regression shrinkage.
plot(lassoTrain, xvar = "lambda", label = TRUE, main = "Ridge Regression")
```
### Forward Step LM using AIC
```{r}
empty = lm(SalePrice ~ 1, data = trainClean[, -3])
full = lm(SalePrice ~ ., data = trainClean[, -3])
scope = list(lower = formula(empty), upper = formula(full))
forwardAic = step(empty, scope, direction = "both", k = 2)
backwardAic = step(full, scope, direction = "both", k = 2)
forwardBIC = step(empty, scope, direction = "both", k = log(nrow(trainClean)))
backwardBIC = step(empty, scope, direction = "both", k = log(nrow(trainClean)))
```

### Everything caret
```{r}
library(caretEnsemble)
library(RANN)
library(skimr)
trainProcessed = preProcess(trainClean[, -ncol(trainClean)],
                            method = c("knnImpute",
                                       "YeoJohnson",
                                       "center",
                                       "scale",
                                       "corr"),
                            k = 38)
trainImputed = predict(trainProcessed, newdata = trainClean)
trainImputed$SalePrice = trainClean$SalePrice

trainControl <- trainControl(method="cv",
                             number = 5,
                             savePredictions = TRUE,
                             allowParallel = TRUE)

modelGBM = train(data = trainImputed,
                 SalePrice ~ .,
                 method = "gbm",
                 trControl = trainControl)

modelKNN = train(data = trainImputed,
                 SalePrice ~ .,
                 method = "knn",
                 trControl = trainControl)

modelRF = train(data = trainImputed,
                 SalePrice ~ .,
                 method = "rf",
                 trControl = trainControl)

modelXGBTree = train(data = trainImputed,
                 SalePrice ~ .,
                 method = "xgbTree",
                 trControl = trainControl)

modelLM = train(data = trainImputed,
                 SalePrice ~ .,
                 method = 'leapSeq',
                 trControl = trainControl)

modelSVM = train(data = trainImputed,
                 SalePrice ~ .,
                 method = 'svmPoly',
                 trControl = trainControl)

models_compare <- resamples(list(GBM=modelGBM, RF=modelRF, KNN = modelKNN, xgb=modelXGBTree, LM = modelLM, SVM = modelSVM))

summary(models_compare)
modelCor(models_compare)

listControl = trainControl(method="repeatedcv",
                           number=10,
                           repeats=3,
                           savePredictions=TRUE,
                           allowParallel = TRUE)
set.seed(4)
modelList = caretList(SalePrice ~ .,
          data = trainImputed,
          trControl = listControl,
          methodList = c('leapSeq',
                         "gbm",
                         "rf",
                         "xgbTree"))

modelList %>% resamples() %>% summary()
modelList %>% resamples() %>% modelCor()

stackControl = trainControl(method="repeatedcv",
                           number=10,
                           repeats=3,
                           savePredictions=TRUE,
                           allowParallel = TRUE)
set.seed(4)
stackModel = caretStack(modelList,
                        method = "xgbDART",
                        metric = "RMSE",
                        trControl = stackControl)

testProcess = predict(trainProcessed, newdata = testClean)
prediction = predict(stackModel, newdata = testProcess)

submission = data_frame(Id = 1461:(length(prediction)+1460),
                        SalePrice = prediction %>% exp() %>% round(digits = -2))


```

